### 2023-01-31 Documentation/UFMG/Relatorio_3/Summary/Summary.tex
report 3

Industrial applications demand automated stabilization of a spray mode.
This can be achieved by a closed-loop control system.
Automated classification of the spray mode is a crucial part of a control system same as the development of an appropriate control algorithm. 
Signal processing implementations of previous projects of the NHL Stenden Water Technology group are showing good classification results.
Further research is necessary to improve the classification accuracy and research and implementation of a suitable classification algorithm. 
Because of that, the work will be done by the Water Technology Group at NHL Stenden University of Applied Sciences and in combination with Dutch companies to match analysis possibilities with knowledge and infrastructure availability.

The setup used for this project can be seen in the Figure 2. To run the experiment automatically it is used a computational processing machine to integrate the peripherals and run their routines, system sensors such as the oscilloscope and the high speed camera 
and also the system actuators which is represented by the high voltage power supply and the syringe pump.

% \begin{figure}[H]
%     \center
%     \includegraphics[width=12cm]{images/images_folder_1/system_design.png}
%     \caption{System Architecture}
% \end{figure}

>>>>

Industrial applications demand automated stabilization of a spray mode.
This can be achieved by a closed-loop control system. Figure 2 shows the control model implemented in this project.

\begin{figure}[H]
    \center
    \includegraphics[width=14cm]{images/software-design.png}
    \caption{Control model implemented in software}
\end{figure}

The setup used for this project can be seen in the Figure 3 and 4. To run the experiment automatically it is used a computational processing machine to integrate the peripherals and run their routines, system sensors such as the oscilloscope and the high speed camera 
and also the system actuators which is represented by the high voltage power supply and the syringe pump.

\begin{figure}[H]
    \center
    \includegraphics[width=10cm]{images/system_setup.png}
    \caption{System Diagram}
\end{figure}

\begin{figure}[H]
    \center
    \includegraphics[width=14cm]{images/system-design.png}
    \caption{System Automation Diagram}
\end{figure}

Automated classification of the spray mode is a crucial part of a control system same as the development of an appropriate control algorithm. 
Signal processing implementations of previous projects of the NHL Stenden Water Technology group are showing good classification results.
Further research is necessary to improve the classification accuracy and research and implementation of a suitable classification algorithm. 
Because of that, this work is being done by the Water Technology Group at NHL Stenden University of Applied Sciences and in combination with Dutch companies to match analysis possibilities with knowledge and infrastructure availability.
